# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data 
```{r loaddata, echo=TRUE}
setwd("C:/Users/ycheng10/Documents/")
if(!file.exists('activity.csv')) {
        unzip("repdata_data_activity.zip")
}
Data <- read.csv('activity.csv')
head(Data)
```

## What is mean total number of steps taken per day?

Sum steps by day, create Histogram, and calculate mean and median.
```{r StepPerday} 
library(ggplot2)
library(scales)
library(Hmisc)
stepsperDay <- tapply(Data$steps, Data$date, sum, na.rm=TRUE)
qplot(stepsperDay, binwidth=500, xlab='Total number of steps per day', ylab='Frequency')
Mean <- mean(stepsperDay)
Median <- median(stepsperDay)
```
The `Mean` is `r Mean` and the `Median` is `r Median`.


## What is the average daily activity pattern?
```{r AvgDailyActivity} 
AvgstepsByInterval <- aggregate(steps ~ interval, Data, mean,na.rm=TRUE)
plot(AvgstepsByInterval$interval,AvgstepsByInterval$steps, type="l", xlab="5 Minute Interval", ylab="Average Number of Steps",main="Average daily activity pattern")
maxInterval <- AvgstepsByInterval[which.max(AvgstepsByInterval$steps),1]
```
Interval with Maximum number of step is: `r maxInterval`


## Imputing missing values
#####  Calculate and report the total number of missing values in the dataset 
```{r}
MissingValues <- length(which(is.na(Data$steps)))
```

Number of missing values: `r MissingValues`

##### Devise a strategy for filling in all of the missing values in the dataset.
##### Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r}
activityDataImputed <- Data
activityDataImputed$steps <- impute(Data$steps, fun=mean)
```


##### Make a histogram of the total number of steps taken each day 
```{r}
stepsByDayImputed <- tapply(activityDataImputed$steps, activityDataImputed$date, sum)
qplot(stepsByDayImputed, xlab='Total steps per day (Imputed)', ylab='Frequency using binwith 500', binwidth=500)
```

##### ... and Calculate and report the mean and median total number of steps taken per day. 
```{r}
stepsByDayMeanImputed <- mean(stepsByDayImputed)
stepsByDayMedianImputed <- median(stepsByDayImputed)

```
Mean (Imputed): `r stepsByDayMeanImputed`
Median (Imputed):  `r stepsByDayMedianImputed`


## Are there differences in activity patterns between weekdays and weekends?
