# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data 
```{r loaddata, echo=TRUE}
setwd("C:/Users/ycheng10/Documents/")
if(!file.exists('activity.csv')) {
        unzip("repdata_data_activity.zip")
}
Data <- read.csv('activity.csv')
head(Data)
```

## What is mean total number of steps taken per day?

Sum steps by day, create Histogram, and calculate mean and median.
```{r StepPerday} 
library(ggplot2)
stepsperDay <- tapply(Data$steps, Data$date, sum, na.rm=TRUE)
qplot(stepsperDay, binwidth=500, xlab='Total number of steps per day', ylab='Frequency')
Mean <- mean(stepsperDay)
Median <- median(stepsperDay)
```
The `Mean` is `r Mean` and the `Median` is `r Median`.


## What is the average daily activity pattern?
```{r AvgDailyActivity} 
AvgstepsByInterval <- aggregate(steps ~ interval, Data, mean,na.rm=TRUE)
plot(AvgstepsByInterval$interval,AvgstepsByInterval$steps, type="l", xlab="5 Minute Interval", ylab="Average Number of Steps",main="Average daily activity pattern")
maxInterval <- AvgstepsByInterval[which.max(AvgstepsByInterval$steps),1]
```
Maximum number of step is: `r maxInterval`

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
